---
title: "Lab8"
author: "Natalie Palmer"
date: "4/4/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Consider a 2x2 design. Assume the DV is measured from a normal distribution with mean 0, and standard deviation 1. Assume that the main effect of A causes a total shift of .5 standard deviations of the mean between the levels. Assume that level 1 of B is a control, where you expect to measure the standard effect of A. Assume that level 2 of B is an experimental factor intended to reduce the effect of A by .25 standard deviations.
  A. create a ggplot2 figure that depicts the expected results from this design 
  B. How many subjects are needed to detect the main effect of A with power = .8? 
  C. How many subjects are needed to detect the interaction effect with power = .8? 
  
```{r}

#load libraries
library(tibble)
library(ggplot2)
library(patchwork)

# define 2-factor score model
mean <- 0
sd <- 1
A <- c(0,5,10,15,20,25,50)
B <- c(0,5,-15)
AB <- rep(0,length(A)*length(B))




```
  
